% Document Class
\documentclass{article}

% Page dimensions
\usepackage[a4paper, total={6in, 8in}]{geometry}

% Empty lines are linebreaks
\usepackage{parskip}

% Language of the document
\usepackage[english]{babel}
\usepackage[babel=true]{csquotes}
% chktex-file 18
\MakeOuterQuote{"}

% Exclude only one word on one page
\clubpenalty=10000 % Exclude cobblers
\widowpenalty=10000 % Exclude whore children

% Remove the indentation at the beginning of the line
\usepackage{lipsum}
\setlength{\parindent}{0pt} 

% Define citation
\usepackage[square, sort, numbers]{natbib}

% Do not highlight the links
\usepackage[breaklinks]{hyperref}
\hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0}}

% Sans-Serif font as a default
\renewcommand{\familydefault}{\sfdefault}

% Number of pages on the front page
\patchcmd{\titlepage}
  {\thispagestyle{empty}}
  {\thispagestyle{plain}}
  {}
  {}
  
% Padding for tables
\usepackage{booktabs}

% Calc project plan dynamically
\usepackage{advdate}

% More line-height
\renewcommand*\baselinestretch{1.3}\selectfont

% IMPORT CUSTOM PACKAGES HERE
\usepackage{import}

% Import Glossary Package
\usepackage{packages/glossary}

% Commands
\newcommand{\newcommentblock}[1]{} % Comment block

% Variables
\newcommand{\thesis}{How to solve the practice-theory gap in adopting an agile project management strategy for larger software businesses?}
\newcommentblock{
  How to solve the practice-theory gap in adopting an agile project management strategy for larger software businesses in the context of scrum?
  Wie lässt sich die Praxis-Theorie-Lücke bei der Einführung einer agilen Projektmanagementstrategie für größere Softwareunternehmen schließen?
  How to solve the practice-theory gap in adopting an agile project management strategy for larger software businesses?
  scope?
  fix the mindset
  kleine haben ja keine probleme 
  mittelständige/größere Unternehmen
  Why do larger software companies find it so difficult to successfully integrate agile as a project management strategy?
  Why do larger software companies find it so difficult to successfully integrate SCRUM as a framework?
  How should SCRUM, as an agile framework, be integrated?
  Why does just integrating SCRUM lead to nothing?
  Why agile frameworks like scrum are not agile
  SCRUM is not agile?
  Is SCRUM agile enough?
  How unflexible can frameworks like SCRUM be until they are no longer agile?
  Why SCRUM is agile on paper but not in practice?
  Why using SCRUM and agile interchangeable is wrong?
  How to make SCRUM, an agile framework, actually agile?
  Merging Human-computer interaction with agile software development
  Closing the gap between theory and practice?
}


% Document structure
\begin{document}
\pagenumbering{Roman}
\setcounter{page}{1}
\input{./chapters/1-titlepage}

\pagenumbering{arabic}
\input{./chapters/2-tags}
\input{./chapters/3-motivation}
\input{./chapters/4-status-quo}
\input{./chapters/5-thesis}
\input{./chapters/6-plan}
\input{./chapters/7-timetable}
\newpage
\pagenumbering{Roman}
\setcounter{page}{2}
\input{./chapters/8-glossary}
\newpage
\input{./chapters/9-references}
\end{document}
