Clients (Product Owners):
The Contractor is from now on called client or business owner/ product owner.

Users/Shoppers:
Customers of the software product are called shoppers or users.

User Stories vs Business Stories:
User stories usually indicate a solution
Wrong approach:
Better approach would be the technology independent of companies, for example, the real problem of a user -> This enables much more far more solutions and more value for the company

Epics, Features, Stories:

Atomic Design:

Project Managers:
project manager has two primary goals: ensuring that there are clearly defined project objectives and parameters and that the project team meets the objectives.

Product Managers:
The role of a product manager is to ensure product success throughout the entire product life cycle, during and beyond the initial project.

Designers:
User Expierence Designer
User Interface Designer

Developer:
Software Architects
Software Designer/System Designers
Software Engineer
Software Developer

Lean Philosophy:\\
Its about minimising waste. Using automation. Using just-in-time/real-time production (using only what you know right now).

Continuous Evolution: 
Products don't start their live after the project finishes.\\
They start it at the moment of creation and evolve over time.
(Familier with continuous design, development, delivery or evolutionary design (design during development))
By monitoring and measuring the customer experience, acting on the real-time data, continuously designing, and continuously delivering to the live environment, we truly can exist in a post-project world of continuous evolution